Analyse gender in music psychology from journal publication data

### 2025-09-19 manuscript/_figure1.qmd
Added a table and rewrote conclusions, polished keywords, and highlighted issues that need attention

fig1 <- ggplot(annual2,aes(x=YearRange,y=Odds_ratio,color=Type,group=Type,shape=separator))+
  #facet_wrap(~TypeGroup,nrow = 2)+
  geom_hline(yintercept=1, linetype="dashed", color = "black") +
  geom_point(position = position_dodge(width = 0.4),show.legend=TRUE,size=3)+
  geom_errorbar(aes(ymin=CI_low,ymax=CI_high),width=0.2,position = position_dodge(width = 0.4))+
#  geom_line(alpha = 0.2,position = position_dodge(width = 0.4))+
  scale_shape_manual(name="Authorship\ntype",values = c(22, 16),guide = "none") +
  scale_color_manual(name="Authorship\ntype",values=custom_palette) +
  xlab('Year range')+
  ylab('Female Authorship Odds Ratio (95%CI)')+
  theme_classic(base_size = 15)
print(fig1)

>>>>

#annual2$Type[1:4]<-NA
annual3<-dplyr::filter(annual2,YearRange!="Overall")
#annual3<-annual2
#annual3$Type[1:4]<-NA

fig1 <- ggplot(annual2,aes(x=YearRange,y=Odds_ratio,color=Type,group=Type,shape=separator))+
  #facet_wrap(~TypeGroup,nrow = 2)+
  geom_hline(yintercept=1, linetype="dashed", color = "black") +
  geom_point(position = position_dodge(width = 0.4),show.legend=TRUE,size=3)+
  geom_errorbar(aes(ymin=CI_low,ymax=CI_high),width=0.2,position = position_dodge(width = 0.4))+
  geom_line(data=annual3,aes(x=YearRange,y=Odds_ratio,color=Type,group=Type,shape=separator),alpha = 0.75,position = position_dodge(width = 0.4))+
  scale_shape_manual(name="Authorship\ntype",values = c(22, 16),guide = "none") +
  scale_color_manual(name="Authorship\ntype",values=custom_palette) +
  xlab('Year range')+
  ylab('Female Authorship Odds Ratio (95%CI)')+
  theme_classic(base_size = 15)
print(fig1)
